OpenMPIR

### 2017-10-08 paper.tex
Fixed double words

In this section we further discuss a significant challenge in HPC:
fragmentation of parallel programming models. There are many ways to write
parallel programs~\cite{openmp, qthreads, chapel, cilk, kokkos, legion, upc,
mpi}.  From libraries, to language extensions, to standalone languages, to
combinations of the these, the fragmentation of parallel programming models is a
problem that is only getting worse. This means that when writing tooling,
optimizations, or analyses, one much choose which model to target as well as
understand points of contention and interoperability between them. A common
difficulty among all of these is that reasoning about parallel programs is hard
and compilers can potentially help reduce this burden. This is exactly
analogous to the problem LLVM solves: compiler optimizations are hard, so
sharing them is valuable. Tapir is a demonstration that the LLVM approach to
compilation of serial code can be effectively extended to help reason about
parallel code.

@@

There are other issues that had to be overcome to run full OpenMP programs
using Tapir. Generally, in addition the the \texttt{task} 
and \texttt{taskwait} pragmas, a program must contain pragmas to initialize OpenMP.
A standard pattern for building task-parallel OpenMP programs is to insert a
\texttt{parallel} pragma to start the necessary hardware threads, followed
immediately by a \texttt{single} pragma to have only one thread continue on the
specified statement. Then the other threads will get work from spawned tasks
instead of implicitly executing the same code in a data parallel manner. For
the purpose of this work we took the shortcut of replacing these pragmas with
no-ops. This worked well for all examples except for one in which after the
\texttt{parallel} and \texttt{single} pragmas the top level task was called
with an unnecessary \texttt{task} pragma.  Because the wait was implicit and
unhandled by our implementation, the simple fix was to remove the \texttt{task}
pragma. This was the only change required to the source code. Our temporary
no-op shortcut, of course, doesn't follow the OpenMP specification, and should
be addressed by future work. Section~\ref{Sec:Future} discusses how how the
implementation can be improved.

>>>>

In this section we further discuss a significant challenge in HPC:
fragmentation of parallel programming models. There are many ways to write
parallel programs~\cite{openmp, qthreads, chapel, cilk, kokkos, legion, upc,
mpi}.  From libraries, to language extensions, to standalone languages, to
combinations of these, the fragmentation of parallel programming models is a
problem that is only getting worse. This means that when writing tooling,
optimizations, or analyses, one much choose which model to target as well as
understand points of contention and interoperability between them. A common
difficulty among all of these is that reasoning about parallel programs is hard
and compilers can potentially help reduce this burden. This is exactly
analogous to the problem LLVM solves: compiler optimizations are hard, so
sharing them is valuable. Tapir is a demonstration that the LLVM approach to
compilation of serial code can be effectively extended to help reason about
parallel code.

@@

There are other issues that had to be overcome to run full OpenMP programs
using Tapir. Generally, in addition the \texttt{task} and \texttt{taskwait}
pragmas, a program must contain pragmas to initialize OpenMP.  A standard
pattern for building task-parallel OpenMP programs is to insert a
\texttt{parallel} pragma to start the necessary hardware threads, followed
immediately by a \texttt{single} pragma to have only one thread continue on the
specified statement. Then the other threads will get work from spawned tasks
instead of implicitly executing the same code in a data parallel manner. For
the purpose of this work we took the shortcut of replacing these pragmas with
no-ops. This worked well for all examples except for one in which after the
\texttt{parallel} and \texttt{single} pragmas the top level task was called
with an unnecessary \texttt{task} pragma.  Because the wait was implicit and
unhandled by our implementation, the simple fix was to remove the \texttt{task}
pragma. This was the only change required to the source code. Our temporary
no-op shortcut, of course, doesn't follow the OpenMP specification, and should
be addressed by future work. Section~\ref{Sec:Future} discusses how the
implementation can be improved.
